SBML L3 paper response to reviewers

### 2020-01-02 main.tex
Final answers

% We have added a some additional text in the ``Introduction'' and ``Impact of SBML'' sections about the general benefits of reproducibility, and advantages of persistent storage

@@

Thank you for this question, which points out that this issue was not addressed sufficiently.  We have now expanded a paragraph in the section titled ``SBML Level 3's modularity and breadth'' to discuss how building on top of an existing format offers advantages over developing a separate format.

@@

These are interesting points.  However, we feel we cannot adequately expand on these issues in this article, both due to space limitations and time limitations, so we have removed the problematic statements to avoid potentially misleading claims.

>>>>

Thank you for raising this issue.  This is, unfortunately, a difficult point to address with SBML because its needs have been largely driven on demand in a bottom-up fashion, with proposals for features and packages coming when people felt the need or desire.  Consequently, we are not sure how to give explicit ``criteria for language standardization'' in the sense described above.  Nevertheless, we have added text to try to help address the issue: (a) in the introduction, we added text that mentions how SBML's popularity led to communities of modelers asking whether it could be expanded or adapted to more cases; and (b) in the section titled ``SBML Level 3's modularity and breadth'', the new fourth paragraph discusses benefits of building on SBML rather than creating a new format.

@@

Thank you for this question, which points out that this issue was not addressed sufficiently in the original manuscript.  We have now expanded a paragraph in the section titled ``SBML Level 3's modularity and breadth'' to discuss how building on top of an existing format offers advantages over developing a separate format.

@@

Thank you for this perspective.  We struggled with how to address this better, but ultimately we concluded that we cannot adequately expand on these issues in this article, both due to space limitations and time limitations.  We have removed the problematic statements to avoid potentially misleading claims.  We hope that a future publication can explore this and related topics more deeply.
